Approximation as Differentiation

### 2025-06-18 main/first-order.tex
Doesn't quite make sense what I've written..
Some progress, notationally a bit tricky...

To interpret the syntactic type constructor $\synVar{L}$, we note that $\LatGal$ has a lifting monad
$\mathcal{L}$ which sends any bounded lattice $X = (X, \meet, \join, \top, \bot)$ to the lattice
$\mathcal{L}(X) = X_\bot$.

>>>>

To interpret the syntactic type constructor $\synVar{L}$, consider the functor $\mathcal{L}$ which extends any
poset $X$ with a distinguished bottom element $\bot$ and any monotone function $f$ between posets with a
mapping from $\bot$ to $\bot$. $\mathcal{L}$ extends to a strong monad $\mathcal{L}^\meet$ on
meet-semilattices, and to a costrong comonad $\mathcal{L}^\join$ on bounded join-semilattices; the bottom
element of $X$ is needed to implement the counit $\varepsilon_X: \mathcal{L}^\join(X) \to X$. These two in
turn form a strong monad in $\LatGal$ with unit $\varepsilon^\join_X \dashv \eta^\meet_X$ and multiplication
$\delta^\join_X \dashv \mu^\meet_X$.
